The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-12 manuscript/manuscript.Rnw
subset PAG gene tree

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PAG2" & species=="bos taurus",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,min.fpkm=1)
@ 
\caption{\genetreeexplanation{\cow \textit{PAG2}}}
\label{fig:pag2_evolution_tree}
\end{figure}

>>>>

tree.id <-
    genes.to.tree[combined.fpkm[gene_short_name=="PAG2" & species=="bos taurus",gene_id],tree]
gene.tree.table <- trees[[tree.id]]$table
gene.tree.expression <- combined.fpkm[gene_id %in% gene.tree.table[,gene_id]]
gene.tree <- read.tree(text=trees[[tree.id]]$tree.dat)
plot.tree.matrix(read.tree(text=trees[[tree.id]]$tree.dat),
                 gene.tree.table,gene.tree.expression,min.fpkm=1,
                 subtree=c("ENSSSCG00000006792",
                           "ENSBTAG00000046085")
                 )
@ 
\caption{\genetreeexplanation{\cow \textit{PAG2}}}
\label{fig:pag2_evolution_tree}
\end{figure}
